---
title: "Mario Kart (5-25-21)"
author: "Eli"
date: "5/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r}
library(tidyverse)
library(skimr)
library(lubridate)
library(ggplot2)
library(gganimate)
library(gifski)
library(png)
library(transformr)
```

Read in data
```{r}
records <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/records.csv')
drivers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-25/drivers.csv')
```


```{r}
glimpse(drivers)
```

```{r}
skim(drivers)
```

```{r}
ThreeLap <- records %>% 
  filter(type == 'Three Lap') %>% 
  mutate(Year = year(date), ImprovementTime = diff(time))
```
Trying to make line graph with 16 different lines, one for each course and the course time over time.
#Shortcuts are causing the zigzag shape- need to remove shortcut times
Take out shortcut times
```{r}
ThreeLapNoShort <- filter(ThreeLap, shortcut == 'No')
```


```{r}
ggplot(ThreeLap, aes(date, time, color = track))+
  geom_line()
ggplot(ThreeLapNoShort, aes(date, time, color = track))+
  geom_line()
#The time changes are so small!
```

Take differences
```{r}
ThreeLapNoShort <- group_by(ThreeLapNoShort,track) %>% 
  mutate(ImprovementTime = abs(time-lag(time,default = first(time))))
```

Get Cumalitive Sum grouped by track
```{r}
ThreeLapNoShort <- ThreeLapNoShort %>% 
  group_by(track) %>% 
  mutate(CumalitiveImprovement = cumsum(ImprovementTime))
```

Graph Improvement Times!
Facet Wrapped By Track
```{r}
ggplot(ThreeLapNoShort, aes(date, CumalitiveImprovement))+
  geom_line()+
  ggtitle("Mario Kart World Record Improvement Times (No Shortcuts)")+
  ylab('Cumalitve Improvement (seconds)')+
  facet_wrap(~track)

ggsave('ImprovementTimesFacet.png')
```
Plotting all lines on one graph
```{r}
ggplot(ThreeLapNoShort, aes(date, CumalitiveImprovement, color = track))+
  geom_line()+
  ggtitle("Mario Kart World Record Improvement Times (No Shortcuts)")+
  ylab('Cumalitve Improvement (seconds)')

ggsave('ImprovementTimesOneGraph.png')
```

Now trying to animate graph
#I don't think I can transition by day, so going to find max times for each year
```{r}
maxTimes <- ThreeLapNoShort %>% 
  group_by(track, Year) %>% 
  summarise(Time = min(time))
```
```{r}
ggplot(maxTimes, aes(Year, Time, color = track))+
  geom_line()#+
  #transition_reveal(Year)
```

#I think I want to look at average time someone held a record OR average time in days a map record held by map

```{r}
AverageRecordHold <- records %>% 
  group_by(track) %>% 
  summarise(AverageRecordDuration = mean(record_duration))
```

